---
title: "Flights"
format: html
editor: visual
date: "April 22, 2023"
execute:
  keep-md: true
  format:
  html:
    code-fold: true
    code-line-numbers: true
---


```{r,Warning=FALSE,Message=FALSE}
library(tidyverse)
library(nycflights13)
library(ggplot2)
library(pander)
library(DT)
```

## Summary

I chose the Flight Carrier and the Delay Arrival Time as the topic of this assignment. I personally have experienced some plane delays and know the painfulness of having to stay in the airport for a longer time than expected. Therefore, I thought knowing the flight carrier that avoid the arrival delay well can be helpful for every person who travel with air planes.

```{r}
fl1<-flights%>%select(c(carrier,arr_delay))%>%filter(arr_delay!="NA")
```

## First Variable -- Carrier

```{r}
table(fl1$carrier)%>%pander
```

## Second Variable -- Arrival Delay Time (min) {.tabset}

### Hide

### Show

```{r, Warning=FALSE}
fl3<-fl1%>%select(arr_delay)
datatable(fl3)
```
##

## Combination of the Two Variables
```{r}
ggplot(fl1, aes(x=factor(carrier), y=arr_delay))+
geom_boxplot(fill="skyblue", color="black")+
ylim(-87,1273)
```


## Conclusion

Looks like AS, HA, and OO Carriers are doing comparily well on not having so much delay on arrival.


```{r}
#| warning: false
#| echo: false
```

